---
title: "Lab 3 Report"
author: "Dontae Jonson"
date: "`r format(Sys.Date())`"
output: github_document
---

Instructions for this lab report can be found on [Your assignment section of Lab Assignment 3 Introduction to ggplot2](https://biol275-msum.github.io/introduction-to-ggplot2.html#your-assignment) on the lab website.

## Fireflies

> A. Insert an R code chunk and create a graph depicting the frequency distribution of the 35 mass measurements. It should have legible text and appropriate axis labels.
```{r}
# Loading packages  --------------------------------------------------------------

library(tidyverse)

# Reading Data ----------------------------------------------------------

fire_data <- read_csv("https://whitlockschluter.zoology.ubc.ca/wp-content/data/chapter02/chap02q19FireflySpermatophoreMass.csv")
fire_data #making sure data was loaded correctly 

# First plot --------------------------------------------------------------

ggplot(data=fire_data) # Make a blank graph
ggplot(data = fire_data) + # Histogram addition
  geom_histogram(mapping = aes(x = spermatophoreMass))


# Cleaning up the graph ----------------------------------------------------

ggplot(data = fire_data) +
  geom_histogram(mapping = aes(x = spermatophoreMass), binwidth = 0.02) +
  labs(x = "spermatophoreMass", y = "Count (Number of Males)")
```



> B. What type of graph did you choose in part (A)? Why?

Histogram. I chose this because there was only one numerical variable. 

> C. Describe the shape of the frequency distribution. What are its main features?

Right skewed. And location is 

> D. What term would be used to describe the largest measurement in the frequency distribution? You can refer to the lecture slides, your notes, or the textbook.

Outlier

## Bird orders

I read the data using the code provided by the instructor. The dataset is from the auk package and was originally named ebird_taxonomy. I converted it to a tibble, removed non-species taxa, and named the new dataset birds.

```{r}
library(auk)                          # load the auk package
birds <- ebird_taxonomy %>%           # start with the ebird_taxonomy data
  as_tibble() %>%                     # tibbles print better in the console
  filter(category == "species")       # remove non-species taxa
```

> E. How many bird species are in the new birds dataset? How did you find out?
10,721

> H. How many orders are there? You can get this right by counting on the graph, but you will only get full points if you use some code to figure it out.

41

> F. Insert an R code chunk and create a graph depicting the distribution of orders in the birds dataset. Sort the orders with the most frequent on the left. It should have legible text and appropriate axis labels.

```{r}
ggplot(data=birds)
ggplot(data=birds)+
  geom_bar(mapping = aes(x =order))#had to put this hear didnt know how to put it in its own code chunk

ggplot(data=birds)+
geom_bar(mapping = aes(x = fct_infreq(order)))+
  labs(x="order") +
  theme_classic(base_size = 7) +
  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(color = "blue", size = rel(1)),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.ticks.x = element_blank()
  )
```


> G. What kind of graph did you create? Why?

I created a bar chart. I did this because it was counting the individual frequencies of categorical events.

## Links to peer review

I didnt review any lab reports as this assignment was turned in late 

## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```

